Astr 513: Final Project

### 2016-05-07 Final_Project/ms.tex
Rearranged chain folders. Wrote the best fit plot script. Added the best fit plot for betoule to the paper.

>>>>

\begin{figure}
  \centering
  \includegraphics[width=0.5\linewidth]{figures/betoule_wcdm_withprior_bestfit.eps}
  \caption{Best fit model of the \citet{betoule2014} data including the
    \Planck priors for a wCDM model. Blue points are the data with
    error bars corresponding to the diagonal of the provided covariance martrix.
    The solid black line is the most likely model from our MCMC chain.}
  \label{fig:betoule_wcdm_noprior_bestfit}
\end{figure}
